D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-09 ootavacuous.tex
Add subsections in OOTA Definition
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

@@

In this case, is the semantic dependency from \co{y} to \co{x},
from \co{z} to \co{x}, or both \co{y} and \co{z} to \co{x}?
Or is this a free choice on the part of the implementation?

And perhaps worse:

@@

Here, the presence or absence of a semantic dependency from \co{y} to
\co{x} depends not only on the value of \co{z}, but also the code in
a horribly complex function.

@@

All of these tools can incur high overhead, especially manual code
inspection.
However, as we will see, C++ implementations need not use these tools.
Their current analysis is guaranteed to be sufficient, courtesy of the
real-world constraints discussed in the next section.
Furthermore, as we will also see, in some special but commonly occurring
circumstances, much simpler methods exist that incur negligible overhead.

@@

% Additional snark:
% "This work reduces the problem of OOTA analysis to that of sequential
%	program analysis.  If you expect better verification of concurrent
%	code than of sequential code, you are in an intellectual state
%	of sin."
5 "Forcing relaxed loads to be ordered before subsequent relaxed stores
%	is an expensive no-op."

>>>>

\subsubsection{Semantic Dependencies Are Per Execution}
\label{sec:Semantic Dependencies Are Per Execution}

@@

\subsubsection{Semantic Dependencies Can Be a Choice}
\label{sec:Semantic Dependencies Can Be a Choice}

@@

In this case, is the semantic dependency from \co{y} to \co{x},
from \co{z} to \co{x}, or both \co{y} and \co{z} to \co{x}?
The answer is that this is a free choice on the part of the
implementation.

\subsubsection{Semantic Dependencies Can Be Complex}
\label{sec:Semantic Dependencies Can Be Complex}

Consider this example:

@@

Here, the presence or absence of a semantic dependency from \co{y} to
\co{x} depends not only on the value of \co{z}, but also the code in a
function that, although single threaded, is horribly complex.

@@

\subsubsection{Complex Semantic Dependencies Are a Choice}
\label{sec:Complex Semantic Dependencies Are a Choice}

All of these tools can incur high overhead, especially manual code
inspection.
However, as we will see, the actual C++ implementations themselves need
not use these tools.
Their current analysis is guaranteed to be sufficient, courtesy of the
real-world constraints discussed in the next section.
Furthermore, as we will also see, in some special but commonly occurring
circumstances, there are much simpler methods that incur negligible overhead.

@@

% Additional snark:
% "This work reduces the problem of OOTA analysis to that of sequential
%	program analysis.  If you expect better verification of concurrent
%	code than of sequential code, you are in an intellectual state
%	of sin."
% "Forcing relaxed loads to be ordered before subsequent relaxed stores
%	is an expensive no-op."
% "So you don't want to learn concurrency?  Then I can only suggest
%	that you either move further up the stack or take early
%	retirement."
